% Use either Acknowledgements (acceptable American spelling) 
% or Acknowledgments (acceptable English spelling)
\chapter*{Acknowledgments}
First and foremost, I give all honour and adoration to the Almighty God who made all things possible. In that vein, I deeply express my thanks to Him for this great opportunity to accomplish this long-wished-for dream of obtaining a doctoral degree in Computer Science. This can only be you, who has endowed me with the ability to put things in proper perspective as contained in this dissertation, and for commendable academic excellence in all the courses taken in the course of this program. Also, I am most grateful to Him for His grace upon my family and for seeing us through thus far despite all the challenges of life we went through. Thank you, Lord!

I am equally using this medium to extend my sincere gratitude and acknowledgment to my adviser, Dr. Daryl Hepting. The immense support and constant guidance, mentoring and readjustment of direction provided by Dr. Hepting helped me to complete my Ph.D. degree as anticipated. In addition, I am so privileged that Dr. Hepting gave me the flexibility to explore the research areas that I am interested in and to leverage my skills in the successful completion of this research work. I would also like to acknowledge and thank the entire members of my Ph.D. Committee -- Dr. Dave Gerhard, Dr. Habib Louafi, Dr. Maher Elshakankiri, and Dr. firstname lastname, for the roles they played and their valuable insights and guidance. 

Huge thanks as well to Dr. Malek Mouhoub (Head of Department) for his support and encouragement especially when I was on the verge of changing supervisor upon discovery my research interests. Dr. JingTao Yao is not left out for the acceptance of my PhD application in the first place. I do appreciate the part you played in my life to bring my dream to past. I cannot conclude this acknowledgment without paying special tributes to Dr. Maher Elshakankiri, who has enabled me to discover my potentials and for believing in me to deliver remarkable and award-winning papers on several occasions. Also, I would like to thank everyone who has contributed to this achievement in one way or the other. 

In addition, I will like to especially thank the Faculty of Graduate Studies and Research and Department of Computer Science for the various funding and teaching assistantship opportunities made available to me from inception to the end of the program.

Last but not least, I would like to especially thank my beloved wife, Sade, and our three wonderful children -– Tami, Teni, and Teju, for their unflinching support and encouragement.